### 2018-03-20 Maths Notes/Further Pure/FP2/Polar Coordinates/Polar-Coordinates.tex
FP2 Notes Update
Notes up to date

\documentclass{article}
% main document, called main.tex
\usepackage{pgfplots}
\usepackage{tikz}
\usetikzlibrary{external}
\tikzexternalize[prefix=tikz/] % activate!

\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{titlesec}

@@

>>>>

\documentclass{article}
\usepackage{pgfplots}
\usepackage{tikz}
\usetikzlibrary{external}
\tikzexternalize[prefix=tikz/]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{titlesec}

@@

\section{Integration}
$$\textrm{Area}=\frac{1}{2}\int^\beta_\alpha r^2 \ d\theta$$
Where the area of the sector is bounded by the half lines $\theta=\alpha$ and $\theta=\beta$, the value of $\theta$ must always be in radians.\\
The the radius in this sector must not drop to zero, choose angles so this doesn't happen. Or choose multiple sections and add together, or use symmetry. 
\section{Differentiating Polar Equations to find tangents}
We only find tangents parallel and perpendicular to the initial line.\\
Using the chain rule:
$$\frac{dy}{dx}=\frac{dy}{d\theta}\times\frac{d\theta}{dx}$$
Parallel: $\frac{dy}{d\theta}=0$\\
Perpendicular: $\frac{dx}{d\theta}=0$
\subsection{Example}
$r=a(1+\cos\theta)$\\
Find the coordinates where the tangents are parallel to the initial line with $\theta=0$\\
$$y=r\sin\theta$$
\textcolor{red}{Replace r with $a(1+\cos\theta)$}
$$y=a(\sin\theta+\sin\theta\cos\theta)$$
\textcolor{red}{Now we can find $\frac{dy}{d\theta}$}
$$\frac{dy}{d\theta}=a(\cos\theta+\cos^2\theta-\sin^2\theta)$$
\textcolor{red}{Simplify and set equal to zero}
$$2\cos^2\theta+\cos\theta-1$$
$$0=(2\cos\theta-1)(\cos\theta+1)$$
\textcolor{red}{Find $\cos\theta$, $\theta$ and $r$}
$$\cos\theta \quad \cos\theta=-1$$
$$\theta=\pm\frac{\pi}{3} \quad \theta=\pi$$
$$r=\frac{3a}{2} \quad r=0$$
\subsubsection{Finding the equations of tangents}
$$\textrm{Cartesian equation:} \ y=r\sin\theta$$
$$\textrm{Polar equation:} \ r=y\csc\theta=r\sin\theta\csc\theta$$

### 2018-03-20 Maths Notes/Statistics/S3/Goodness of fit and contingency tables/Goodness of fit and contingency tables.tex
Notes up to date

>>>>

\subsection{Testing the normal distribution as a model}
We would fit data to a normal if:
\begin{itemize}
\item Data is continuous
\item Symmetrical about the mean
\item 68\% of the data falls within 1 standard deviation of the mean
\end{itemize}
\textit{During observations on the height of 200 male students the following data was observed:}\\
\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|X|X|X|X|}
Height (cm)&150-154&155-159&160-164&165-169&170-174&175-179&180-184&185-189&190-194\\
Freq&4&6&12&30&64&52&18&10&4\\
\textit{Test at the 0.05 level of see if the height of the male students could be modelled by a normal distribution with mean 172 and standard deviation 6}\\
\textcolor{red}{State the hypotheses}
$H_0:$ Data can be modelled by a normal distribution $N(172,6^2)$\\
$H_1:$ Data cannot be modelled by this normal distribution
\textcolor{red}{Fill in the below table, calculating the probabilities by finding the z values and converting to probabilities. Find E by multiplying the probability by 200. For the first and last values, find all values past this value}\\
Class&Z upper limit&$P(a<x<b)$&E\\
$<154.5$&-2.92&0.0019&0.38\\
154.5-159.5&-2.08&0.0169&3.38\\
159.5-164.5&-1.25&0.0868&17.36\\
164.5-169.5&-0.42&0.2316&46.32\\
169.5-174.5&0.42&0.3256&65.12\\
174.5-179.5&1.25&0.2316&46.32\\
184.5-189.5&2.92&0.0169&3.38\\
$>189.5$&&0.0019&0.38\\
\textcolor{red}{Remember to combine rows so that all are greater than 5, find $X^2$}
$$X^2=12.1$$
\textcolor{red}{Find the degrees of freedom, subtracting one from the number of combined classes}
\textcolor{red}{Find the value of $\chi^2_4$ at 5\%}
$$\chi^2_4 \ \textrm{At 5\%}=9.488$$
\textcolor{red}{Compare the value of $\chi^2_4$ with the value of $X^2$ and state conclusions}
$$X^2>\chi^2$$
Significant result, reject $H_0$, does not follow a normal distribution

### 2018-03-20 Physics Notes/Nuclear Physics/Nuclear Energy/Nuclear Energy.tex
Notes up to date

>>>>

\item Radioactive waste from fuel rods
\item Waste initially highly radioactive and needs to be remotely handled
\item Waste initially placed in cooling ponds - remove heat and absorb radiation
\item Plutonium/uranium separated to be recycled
\item High level waste is vitrified - In liquid form radiation may leak, stable storage
\item Transported in crash resistant containers for safety
\item Placed in steel containers
\item Stored deep underground
